Current Models

### 2018-07-21 models.Rmd

Generally, ARIMA models are defined according to three model structure 
parameters: the number of autoregressive terms (p), the degree of differencing 
(d), and the order of the moving average (q), and are represented as 
ARIMA(p, q, q) [@Box1970]. While the `auto.arima` function allows for seasonal
models, the seasonality is hard-coded to be on the same period as the sampling,
which is not the case for the Portal rodent surveys. As a result, no seasonal 
models were evaluated. AutoArima is fit flexibly, such that the model 
parameters can vary from fit to fit.

@@

GARCH models are generalized ARMA models and are defined according to their 
link function, response distribution, and two model structure parameters: 
the number of autoregressive terms (p) and the order of the moving average 
(q), and are represented as GARCH(p, q) [@Liboschik2017a]. The PETS model is 
fit using the log link and a Poisson response, as well as with p = 1 
(first-order autoregression) and q = 12 (yearly moving average). The 
environmental variables potentially included in the model are min, mean, and
max temperatures, precipitation, and NDVI.

@@

>>>>

Generally, ARIMA models are defined according to three model structure 
parameters: the number of autoregressive terms (p), the degree of differencing 
(d), and the order of the moving average (q), and are represented as 
ARIMA(p, d, q) [@Box1970]. While the `auto.arima` function allows for seasonal
models, the seasonality is hard-coded to be on the same period as the sampling,
which is not the case for the Portal rodent surveys. As a result, no seasonal 
models were evaluated. AutoArima is fit flexibly, such that the model 
parameters can vary from fit to fit.

@@

GARCH models are generalized ARMA models and are defined according to their 
link function, response distribution, and two model structure parameters: 
the number of autoregressive terms (p) and the order of the moving average 
(q), and are represented as GARCH(p, q) [@Liboschik2017a]. The pevGARCH model 
is fit using the log link and a Poisson response, as well as with p = 1 
(first-order autoregression) and q = 12 (yearly moving average). The 
environmental variables potentially included in the model are min, mean, and
max temperatures, precipitation, and NDVI.

@@

## Ensemble

In addition to the base models, we include an ensemble, constructed using the
base model AIC weights. The ensemble mean is calculated as the AIC-weighted
mean of all model means. The ensemble variance is estimated as the sum of 
the AIC-weighted mean of all model variances and the variance of the estimated
AIC-weighted mean, calculated using the unbiased estimate of sample variances.
